Matching bullets

### 2015-11-16 imaging-paper.Rnw
Address comments, begin discussion of cylindrical fit

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.width=6, out.width='\\textwidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

It's clear that our next approach must be to model the signal in order to focus on the noise, given that the noise should correspond to bullet markings.
\hh{XXX let's not call the markings noise - that has the conotation of them being random. The markings are also a signal, it is just dominated by the stronger signal of the land structure. We often go through a process of multiple steps to get close to the more interesting, smaller signal. }
\hh{XXX on a side note - I've got a different relative path to the x3p bullet files ... should we assume a data directory inside the folder? Then we don't have to push the files on a github repo again, but are using the same file structure?}

>>>>

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

It's clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

\subsection{Cylindrical Fit}

One reasonable approach is to fit a circle to the curve and compute the residuals from this fit. The scatterplot below shows the residuals of such a fit. The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For cross sections of $x$ values between 75 and 80, there is a residual circular structure that does not show up for all cross sections.

<<residual, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 80 & x >=75), y, value-ypred, colour=factor(x)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

<<residual2, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 5), y, value-ypred, colour=factor(x)) +
  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  theme(legend.position="bottom")
@

\hh{XXX on a side note - I've got a different relative path to the x3p bullet files ... should we assume a data directory inside the folder? Then we don't have to push the files on a github repo again, but are using the same file structure?}
